Scientific Reports Title to see here (20 words or less)

### 2016-06-14 draft1.tex
small changes

\author[1,*]{Alice Author}
\author[2]{Bob Author}
\author[1,2,+]{Christine Author}
\author[2,+]{Derek Author}
\affil[1]{Affiliation, department, city, postcode, country}
\affil[2]{Affiliation, department, city, postcode, country}

\affil[*]{corresponding.author@email.example}

\affil[+]{these authors contributed equally to this work}

@@

@@

\subsection*{Multidimensional Optimization}
We used the Julia language POETs package, which combines simulated anealing with Pareto optimality to generate families of best parameters.\cite{bassen2016jupoets} Using the two clusters formed by k-means, we minimized the averaged mean squared error to create these parameter families. We utilized a monotonically decreasing cooling schedule with five iterations at each temperature. The trade off curve generated using $\alpha$ = .9 is shown in \ref{fig:tradeoffcurve}, and with $\alpha$ =.5  in \ref{fig:tradeoffcurveslower}. To decrease the time neccessary to perform the simulated annealing, we utilized Julia's transparent parallization capabilities. With the @parallel (+) operator, we were able to calculate patient's mean squarred errors in parallel. The speed up from parallization is shown in \ref{fig:executiontime}.

>>>>

\author[1]{Rachel LeCover}
\author[1,*]{Jeffrey D. Varner}
\affil[1]{Affiliation, School of Chemical and Biomolecular Engineering, Ithaca NY, 14852, USA}

\affil[*]{jdv27@cornell.edu}

@@

To our knowledge, this is the first study to attempt to model heart rate as a function of blood pressure for such a large number of patients. Additionally, many previous studies were performed with healthy patients, in contrast, this study focuses on intensive care unit patients.

@@

\subsection*{Multidimensional Optimization}
We used the Julia language POETs package, which combines simulated anealing with Pareto optimality to generate families of best parameters.\cite{bassen2016jupoets} Using the two clusters formed by k-means, we minimized the averaged mean squared error to create these parameter families. We utilized a monotonically decreasing cooling schedule with five iterations at each temperature. The trade off curve generated using $\alpha$ = .9 is shown in \ref{fig:tradeoffcurve}, and with $\alpha$ =.5  in \ref{fig:tradeoffcurveslower}. We used the parameter families from the slower cooling for further analysis.

To decrease the time neccessary to perform the simulated annealing, we utilized Julia's transparent parallization capabilities. With the @parallel (+) operator, we were able to calculate patient's mean squarred errors in parallel. The speed up from parallization is shown in \ref{fig:executiontime}.
